### 2015-07-13 narrative/management.tex
spell check

Careful management will be required to ensure that the problems and delays that are inevitable in any research project
do not  disrupt overall progress.Here we define a detailed workplan,
establish a  management structure with defined oversight responsibilities, and establish a schedule of regular meetings and
reviews to ensure progress.  We will use google docs to share documents, emails lists for informal communications and a 
weekly phone call in the main research areas to discuss project tasks and milestones.

>>>>

Careful management will be required to ensure that the problems and delays that are inevitable in any research project
do not  disrupt overall progress.Here we define a detailed work plan,
establish a  management structure with defined oversight responsibilities, and establish a schedule of regular meetings and
reviews to ensure progress.  We will use Google Docs (http://docs.google.com) to share documents, emails lists for informal communications and a 
weekly phone call in the main research areas to discuss project tasks and milestones.
